---
title: "/s/ only data analysis"
author: "Grace Brown"
date: "April 16, 2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("knitr") # for knitting things
library("tidyverse")
library("lme4")
library("lmerTest")
library("ggplot2")
library("MuMIn")
library("brms") # for bayesian model
library("emmeans") # for pairwise comparisons
library("tidybayes") 
library("broom")
library("ggeffects")
library("broom.mixed")
library("patchwork")  # for figure panels


knitr::opts_knit$set(root.dir = "/Users/gracebrown/qp1_2spk")

# color-blind-friendly palette
cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442") 
cbPalette_2 <- c("#0072B2", "#D55E00", "#CC79A7")
cbPalette_3 <-c("#56B4E9", "#009E73", "#F0E442")
theme_set(theme_bw())
```

## Load Data

```{r load}
### DATA WRANGLING
## read messy dataset
df.sibilant <- read_csv("~/qp1_2spk/data/qp1_2spk-merged.csv")
df.survey <- read_csv("~/qp1_2spk/data/survey.csv")
df.phon <- read_csv("~/qp1_2spk/data/phonetic_analysis.csv")

# join survey and sibilant
df.sibilant <- left_join(x = df.sibilant,
                         y = df.survey,
                         by = "workerid")

df.sibilant <- left_join(x = df.sibilant,
                         y = df.phon,
                         by = "stimulus")

# workerid EXCLUSION BY PRE-REGISTERED CRITERIA
## (1) audio attention check 
df.exclude_audio <- df.sibilant %>%  
  filter(trial_type == "audio-button-response", result == "incorrect") %>% 
  distinct(workerid)  # Keep only unique worker IDs

df.sibilant <- df.sibilant %>% 
  anti_join(df.exclude_audio, by = "workerid")

## (2) - responded to less than 85% of trials 
trial_num <- 72 # 72 total trials (36 sib + 36 control)
df.exclude_trialnum <- df.sibilant %>% 
  filter(!is.na(rt), trial_type == "audio-slider-response") %>% 
  count(workerid) %>% 
  filter(n / trial_num < 0.85) %>% 
  distinct(workerid)

df.sibilant <- df.sibilant %>% 
  anti_join(df.exclude_trialnum, by = "workerid")

# SET SRQ SCORES
## set blank items in `coding` to NA
df.sibilant$coding[df.sibilant$coding == ""] <- NA 

## create gender_trans and gender_link srq subscales in dataset 
df.sibilant$gender_trans <- ifelse(df.sibilant$trial_type == "html-slider-response" & 
                              is.na(df.sibilant$coding) == FALSE & 
                              df.sibilant$coding == "NEGATIVE",
                            as.numeric(df.sibilant$response)/100, NA)
df.sibilant$gender_link <- ifelse(df.sibilant$trial_type == "html-slider-response" & 
                             is.na(df.sibilant$coding) == FALSE & 
                             df.sibilant$coding == "POSITIVE",
                           (10000 - as.numeric(df.sibilant$response))/100, NA)

## calculate gender_trans and gender_link scores, merge with df.sibilant 
score_gender_link <- df.sibilant %>% 
  filter(!is.na(gender_link)) %>% 
  group_by(workerid) %>% 
  summarize("score_link" = sum(gender_link))
df.sibilant <- merge(df.sibilant, score_gender_link, by = "workerid", all.x = TRUE)
score_gender_trans <- df.sibilant %>% 
  filter(!is.na(gender_trans)) %>% 
  group_by(workerid) %>% 
  summarize("score_trans" = sum(gender_trans))
df.sibilant <- merge(df.sibilant, score_gender_trans, by = "workerid", all.x = TRUE)

## calculate final srq score
df.sibilant <- df.sibilant %>% mutate("srq_score" = (score_trans+score_link)/13)

# SELECT TRIALS OF INTEREST AND RECODE VARIABLES OF INTEREST
## relabel speaker from numeric ID to letter ID
df.sibilant$spk <- recode(df.sibilant$spk, 
                       `246` = "B", 
                       `723` = "A") %>%
  as.factor() # set to factor

### relabel sib conditions
df.sibilant$sib_code[df.sibilant$sib_code == "low"] = "backed"
df.sibilant$sib_code[df.sibilant$sib_code == "high"] = "fronted"
```
### Create Response-Only Dataframe + New Variables

```{r summarize data}
### summarize numeric data 
df.numeric <- df.sibilant %>% 
  filter(!is.na(response)) %>% 
  filter(trial_type == "audio-slider-response") %>%
  group_by(spk) %>% 
  filter(spk == "A" | spk == "B") 

df.numeric$sib_code <- factor(df.numeric$sib_code, 
                              levels = c("control", 
                                         "backed", 
                                         "mid", 
                                         "fronted"))
df.numeric$response <- as.double(df.numeric$response)/10000 # rescale to 0-1 for ZOIB 

# create normalized phonetic variables + pitch range variable
df.numeric <- df.numeric %>% 
  group_by(spk) %>% 
  mutate(NC_norm_mean_f0 = (NC_pitAve_semi - mean(NC_pitAve_semi))/sd(NC_pitAve_semi),
         NC_norm_SD_f0 = (NC_pitSD_semi - mean(NC_pitSD_semi))/sd(NC_pitSD_semi),
         NC_norm_max_f0 = (NC_pitMax_semi - mean(NC_pitMax_semi))/sd(NC_pitMax_semi),
         NC_norm_min_f0 = (NC_pitMin_semi - mean(NC_pitMin_semi))/sd(NC_pitMin_semi),
         NC_norm_range_f0 = (NC_norm_max_f0 - NC_norm_min_f0), 
         norm_mean_f0 = (pitAve_semi - mean(pitAve_semi))/sd(pitAve_semi),
         norm_SD_f0 = (pitSD_semi - mean(pitSD_semi))/sd(pitSD_semi),
         norm_max_f0 = (pitMax_semi - mean(pitMax_semi))/sd(pitMax_semi),
         norm_min_f0 = (pitMin_semi - mean(pitMin_semi))/sd(pitMin_semi)) %>%
  ungroup()

# create centered variables for statistical analysis
df.numeric <- df.numeric %>% 
  mutate(srq_scoreC = srq_score - mean(srq_score),
         ageC = age - mean(age, na.rm = T),
         NC_norm_mean_f0C = NC_norm_mean_f0 - mean(NC_norm_mean_f0),
         NC_norm_range_f0C = NC_norm_range_f0 - mean(NC_norm_range_f0),
         prop_creakC = prop_creak - mean(prop_creak),
         speech_rateC = speech_rate - mean(speech_rate),
         s_msC = s_milliseconddur - mean(s_milliseconddur, na.rm = T),
         f2_rawC = f2_raw - mean(f2_raw, na.rm = T))

df.numeric <- df.numeric %>% 
  group_by(workerid) %>% 
  mutate(response = (response - mean(response, na.rm = T))/sd(response, na.rm = T)) %>% ungroup()

#### by participant summaries (SECONDARY OUTLIER CHECKPOINT)
df.numeric %>% 
  group_by(workerid) %>% 
  summarize("min" = min(response), 
            "mean" = mean(response), 
            "max" = max(response))

# exclude participants who only responded 0 or 1 for all trials 
df.exclude_outlier <- df.numeric %>%
  group_by(workerid) %>%
  filter(min(response) == 1 | max(response) == 0) %>% 
  distinct(workerid)  # Keep only unique worker IDs

df.numeric <- df.numeric %>% 
  anti_join(df.exclude_outlier, by = "workerid")

# exclude no-response gender id's 
df.exclude_gender <- df.numeric %>%  
  filter(is.na(gender_corr)) %>% 
  distinct(workerid)

df.numeric <- df.numeric %>% 
  anti_join(df.exclude_gender, by = "workerid")
```

## Basic Summaries
### Demographic Data
```{r summaries}
# Gender Summary
df.numeric %>% 
  select(workerid,gender_corr) %>% 
  group_by(gender_corr) %>% 
  reframe("count" = n_distinct(workerid))

# Age Summary
df.numeric %>% 
  filter(!is.na(age)==T) %>% 
  summarize("min_age" = min(age), 
            "mean_age" = mean(age), 
            "max_age" = max(age), 
            "sd_age" = sd(age))

# Racial Summary (flor flavor, not part of planned analysis)
df.numeric %>% 
  select(workerid,race_corr) %>% 
  group_by(race_corr) %>% 
  reframe("count" = n_distinct(workerid))

# Region Summary (for flavor, not part of planned analysis)
df.numeric %>% 
  select(workerid,region) %>% 
  group_by(region) %>% 
  reframe("count" = n_distinct(workerid))

# Education Summary (for flavor, not part of planned analysis)
df.numeric %>% 
  select(workerid,edu) %>% 
  group_by(edu) %>% 
  reframe("count" = n_distinct(workerid))

# Political Summary (for flavor, not part of planned analysis) 
df.numeric %>% 
  select(workerid,political) %>% 
  group_by(political) %>% 
  reframe("count" = n_distinct(workerid))
```

### By Participant Response Summaries (Secondary Outlier Checkpoint!)
```{r by_part}
df.numeric %>% 
  group_by(workerid, spk) %>% 
  summarize("min" = min(response), 
            "mean" = mean(response), 
            "max" = max(response))
```

### By Speaker (Ratings)
```{r by_spk}
#### by spk
df.numeric %>% 
  subset(select = -c(trial_index,
                     workerid)) %>%
  group_by(spk) %>%
  summarize("mean"=mean(response), 
            "var" = var(response), 
            "sd" = sd(response))
```

### By Speaker + Sib (Ratings)
```{r by_spk_sib}
#### by spk + sib 
df.numeric %>% 
  subset(select = -c(trial_index,
                     workerid)) %>%
  group_by(sib_code, spk) %>%
  summarize("mean"=mean(response), 
            "var" = var(response), 
            "sd" = sd(response))
```

### By Speaker + Sib (+ Gender)
```{r by_spk_sib}
#### by spk + sib + gender
df.numeric %>% 
  subset(select = -c(trial_index,
                     workerid)) %>%
  group_by(sib_code, spk, gender_corr) %>%
  summarize("mean"=mean(response), 
            "var" = var(response), 
            "sd" = sd(response))
```

### Summary of Phonetic Analyses by Speaker
```{r by_phon}
#### phonetics by spk 
df.numeric %>% 
  group_by(spk) %>% 
  summarize("meanHz" = mean(pitAve_Hz), 
         "pitSDHz" = mean(pitSD_Hz),
         "meanSem" = mean(pitAve_semi), 
         "pitSDSem" = mean(pitSD_semi),
         "SR" = mean(speech_rate),
         "s_dur" = mean(s_milliseconddur, na.rm = T),
         "prop_creak" = mean(prop_creak))
```

## Visualizations
### General distribution of all ratings
```{r hist_all, echo=FALSE}
fig.hist_all <- ggplot(df.numeric, 
                   aes(x=response)) + 
  geom_histogram(bins=30) +
  xlab("Masculinity Rating") + 
  scale_fill_manual(values = cbPalette) + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
ggsave(file="~/qp1_2spk/analysis/figures/hist_all.pdf",width=7,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/hist_all.png",width=,height=4)
print(fig.hist_all)
```

### Overall distribution of ratings by speaker
```{r hist_spk, echo=FALSE}
fig.hist_by_spk <- ggplot(df.numeric,
                      aes(x=response))+
  geom_histogram(bins=30)+
  facet_grid(.~spk) +
  xlab("Masculinity Rating") +
  scale_fill_manual(values = cbPalette, name = "Speaker ID")
print(fig.hist_by_spk)
ggsave(file="~/qp1_2spk/analysis/figures/hist_spk.pdf",width=7,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/hist_spk.png",width=,height=4)
```

### Overall distribution of ratings by sib_code
```{r hist_by_sib, echo=FALSE}
fig.hist_by_sib <- ggplot(df.numeric,
                      aes(x=response))+
  geom_histogram(bins=30)+
  facet_grid(.~sib_code) +
  xlab("Masculinity Rating")
print(fig.hist_by_sib)
ggsave(file="~/qp1_2spk/analysis/figures/hist_sib.pdf",width=7,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/hist_sib.png",width=,height=4)
```

### Overall distribution of ratings by sib_code and speaker
```{r hist_by_spk_sib, echo=FALSE}
fig.hist_by_spk_sib <- ggplot(df.numeric,
                          aes(x=response))+
  geom_histogram(bins=20)+
  facet_grid(sib_code~spk) +
  xlab("Masculinity Rating")
print(fig.hist_by_spk_sib)
ggsave(file="~/qp1_2spk/analysis/figures/hist_spk_sib.pdf",width=7,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/hist_spk_sib.png",width=,height=4)
```

### Ratings by item (and speaker)
```{r triplet_bar_pretty, echo=FALSE}
#BY SPEAKERS & ITEM (IN PARTS)
## items 1-7
fig.by_item1 <- df.numeric %>% filter(triplet_id < 8) %>%
ggplot(mapping = aes(x = sib_code,
                     y = response)) + 
  stat_summary(fun = "mean",
               geom = "bar",
               fill = "lightblue") + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") +
  facet_grid(triplet_id~spk) +
  scale_x_discrete(limits = c("control", "backed", "mid", "fronted")) + 
  labs(x = "/s/ Condition",
       y = "Masculinity Rating")
print(fig.by_item1)
ggsave(file="~/qp1_2spk/analysis/figures/bar_item1.pdf",width=6,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/bar_item1.png",width=6,height=4)

## items 8-15
fig.by_item2 <- df.numeric %>% filter(triplet_id > 7 & triplet_id < 16) %>%
  ggplot(mapping = aes(x = sib_code,
                     y = response)) + 
  stat_summary(fun = "mean",
               geom = "bar",
               fill = "lightblue") + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") +
  facet_grid(triplet_id~spk) +
  scale_x_discrete(limits = c("control", "backed", "mid", "fronted")) + 
  labs(x = "/s/ Condition",
       y = "Masculinity Rating")
print(fig.by_item2)
ggsave(file="~/qp1_2spk/analysis/figures/bar_item2.pdf",width=6,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/bar_item2.png",width=6,height=4)

## items 16-21
fig.by_item3 <- df.numeric %>% filter(triplet_id > 15) %>%
  ggplot(mapping = aes(x = sib_code,
                     y = response)) + 
  stat_summary(fun = "mean",
               geom = "bar",
               fill = "lightblue") + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") +
  facet_grid(triplet_id~spk) +
  scale_x_discrete(limits = c("control", "backed", "mid", "fronted")) + 
  labs(x = "/s/ Condition",
       y = "Masculinity Rating")
print(fig.by_item3)
ggsave(file="~/qp1_2spk/analysis/figures/bar_item3.pdf",width=6,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/bar_item3.png",width=6,height=4)
```

### Ratings by speaker
```{r spk_bar, echo=FALSE}
## bar graph
fig.bar_spk <- ggplot(data = df.numeric,
       mapping = aes(x = spk,
                     y = response)) + 
  stat_summary(fun = "mean",
               geom = "bar",
               fill = "lightblue") + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") +
  labs(x = "Speaker ID",
       y = "Masculinity Rating")
print(fig.bar_spk)
ggsave(file="~/qp1_2spk/analysis/figures/bar_spk.pdf",width=8,height=5)
ggsave(file="~/qp1_2spk/analysis/figures/bar_spk.png",width=8,height=5)

## individual observations
fig.point_spk <- ggplot(data = df.numeric,
                        mapping = aes(x = spk,
                                      y = response)) + 
  geom_point(alpha = 0.025,
             position = position_jitter(width = 0.1, height = 0)) + 
  stat_summary(fun.data = "mean_cl_boot",
               shape = 21,
               size = 0.5,
               color = "black",
               fill = "lightblue") + 
  labs(x = "Speaker ID",
       y = "Masculinity Rating")
print(fig.point_spk)
ggsave(file="~/qp1_2spk/analysis/figures/point_spk.pdf",width=8,height=5)
ggsave(file="~/qp1_2spk/analysis/figures/point_spk.png",width=8,height=5)
```

### Ratings by sib_code
```{r sib_bar, echo=FALSE}
## bar graph
fig.bar_sib <- ggplot(data = df.numeric,
       mapping = aes(x = sib_code,
                     y = response)) + 
  stat_summary(fun = "mean",
               geom = "bar",
               fill = "lightblue") + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") +
  scale_x_discrete(limits = c("control", "backed", "mid", "fronted")) + 
  #coord_cartesian(ylim = c(0, 0.55)) +
  labs(x = "/s/ Condition",
       y = "Masculinity Rating")
print(fig.bar_sib)
ggsave(file="~/qp1_2spk/analysis/figures/bar_sib.pdf",width=8,height=5)
ggsave(file="~/qp1_2spk/analysis/figures/bar_sib.png",width=8,height=5)

## individual observations
fig.point_sib <- ggplot(data = df.numeric,
       mapping = aes(x = sib_code,
                     y = response)) + 
  geom_point(alpha = 0.025,
             position = position_jitter(width = 0.1, height = 0)) + 
  stat_summary(fun.data = "mean_cl_boot",
               shape = 21,
               size = 0.5,
               color = "black",
               fill = "lightblue") + 
  scale_x_discrete(limits = c("control", "backed", "mid", "fronted")) + 
  labs(x = "/s/ Condition",
       y = "Masculinity Rating")
print(fig.point_sib)
ggsave(file="~/qp1_2spk/analysis/figures/point_sib.pdf",width=8,height=5)
ggsave(file="~/qp1_2spk/analysis/figures/point_sib.png",width=8,height=5)
```

### Ratings by speaker and sibilant
```{r spk_sib_bar, echo=FALSE}
#BY SPEAKERS & SIB CODE
## bar graph
fig.bar_sib_spk <- ggplot(data = df.numeric,
       mapping = aes(x = sib_code,
                     y = response)) + 
  stat_summary(fun = "mean",
               geom = "bar",
               fill = "lightblue") + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") +
  facet_grid(~spk) +
  scale_x_discrete(limits = c("control", "backed", "mid", "fronted")) + 
  labs(x = "/s/ Condition",
       y = "Masculinity Rating")
print(fig.bar_sib_spk)
ggsave(file="~/qp1_2spk/analysis/figures/bar_sib_spk.pdf",width=8,height=5)
ggsave(file="~/qp1_2spk/analysis/figures/bar_sib_spk.png",width=8,height=5)

## individual observations
fig.point_sib_spk <- ggplot(data = df.numeric,
       mapping = aes(x = sib_code,
                     y = response,
                     group = spk)) + 
  geom_point(alpha = 0.025,
             position = position_jitter(width = 0.1, height = 0)) + 
  stat_summary(fun.data = "mean_cl_boot",
               shape = 21,
               size = 0.5,
               color = "black",
               fill = "lightblue") + 
  facet_grid(~spk) + 
  scale_x_discrete(limits = c("control", "backed", "mid", "fronted")) + 
  labs(x = "/s/ Condition",
       y = "Masculinity Rating")
print(fig.point_sib_spk)
ggsave(file="~/qp1_2spk/analysis/figures/point_sib_spk.pdf",width=8,height=5)
ggsave(file="~/qp1_2spk/analysis/figures/point_sib_spk.png",width=8,height=5)
```

#### By Listener Gender
```{r}
fig.by_gender <- ggplot(data = df.numeric,
       mapping = aes(x = sib_code,
                     y = response)) + 
  stat_summary(fun = "mean",
               geom = "bar",
               fill = "lightblue") + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") +
  facet_grid(spk~gender_corr) +
  scale_x_discrete(limits = c("control", "backed", "mid", "fronted")) + 
  labs(x = "/s/ Condition",
       y = "Masculinity Rating",
       title = "Observed Masculinity Ratings")
print(fig.by_gender)
ggsave(file="~/qp1_2spk/analysis/figures/bar_gender.pdf",width=8,height=5)
ggsave(file="~/qp1_2spk/analysis/figures/bar_gender.png",width=8,height=5)

## individual observations
fig.point_by_gender <- ggplot(data = df.numeric,
       mapping = aes(x = sib_code,
                     y = response,
                     group = spk)) + 
  geom_point(alpha = 0.025,
             position = position_jitter(width = 0.1, height = 0)) + 
  stat_summary(fun.data = "mean_cl_boot",
               shape = 21,
               size = 0.5,
               color = "black",
               fill = "lightblue") + 
  facet_grid(gender_corr~spk) + 
  scale_x_discrete(limits = c("control", "backed", "mid", "fronted")) + 
  labs(x = "/s/ Condition",
       y = "Masculinity Rating")
print(fig.point_by_gender)
ggsave(file="~/qp1_2spk/analysis/figures/point_sib_spk.pdf",width=8,height=5)
ggsave(file="~/qp1_2spk/analysis/figures/point_sib_spk.png",width=8,height=5)

fig.by_gender +  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) + fig.point_by_gender + theme(axis.text.x = element_text(angle = 90, vjust = 0.5))
```

### SRQ (SAVE AND PRINT THESE)
```{r srq}
ggplot(df.numeric, 
       mapping = aes(y = response, 
                     x = srq_score)) + 
  stat_summary(aes(group = spk),
               fun = "mean",
               geom = "pointrange",
               alpha = .5) +
  xlab("Participant SRQ Score") +
  ylab("Mean Masculinity Rating") + 
  facet_wrap(~spk) +
  geom_smooth(method = "lm",
              se = T,
              color = "red") +
  scale_color_manual(values = cbPalette_2, name = "Speaker")

ggplot(df.numeric, mapping = aes(y = response, 
                          x = srq_score)) + 
  stat_summary(aes(group = sib_code),
               fun = "mean",
               geom = "pointrange",
               alpha = .5) +
  xlab("Participant SRQ Score") +
  ylab("Mean Masculinity Rating") + 
  facet_wrap(~sib_code) +
  geom_smooth(method = "lm",
              se = T,
              color = "red")

ggplot(df.numeric, mapping = aes(y = response, 
                          x = srq_score)) + 
  stat_summary(aes(group = sib_code),
               fun = "mean",
               geom = "pointrange",
               alpha = .25) +
  xlab("Participant SRQ Score") +
  ylab("Mean Masculinity Rating") + 
  facet_wrap(sib_code~spk) +
  geom_smooth(method = "lm",
              se = T,
              color = "red") +
  scale_color_manual(values = cbPalette, name = "Sibilant Condition")

df.numeric$sib_recode <- recode(df.numeric$sib_code, 
                       `fronted` = "fronted", 
                       `control` = "other",
                       `backed` = "other",
                       `mid` = "other") %>%
  as.factor()

ggplot(df.numeric, mapping = aes(y = response, 
                          x = s_msC)) + 
  stat_summary(aes(group = sib_code),
               fun = "mean",
               geom = "pointrange",
               alpha = .25) +
  xlab("Participant SRQ Score") +
  ylab("Mean Masculinity Rating") + 
  facet_wrap(sib_code~spk) +
  geom_smooth(method = "lm",
              se = T,
              color = "red") +
  scale_color_manual(values = cbPalette, name = "Sibilant Condition")
```

```{r}
ggplot(df.numeric, 
       mapping = aes(y = srq_score,
                     x = gender_corr)) + 
  geom_violin() + 
  stat_summary(fun.data = "mean_cl_boot",
               shape = 21,
               size = 0.5,
               color = "black",
               fill = "lightblue") +
  ylab("Participant SRQ Score") +
  xlab("Participant Gender") 

ggplot(df.numeric, 
       mapping = aes(y = response, 
                     x = srq_score,
                     group = gender_corr)) + 
  stat_summary(fun = "mean",
               geom = "pointrange",
               alpha = .2,
               aes(color = gender_corr)) +
  xlab("Participant SRQ Score") +
  ylab("Mean Masculinity Rating") + 
  facet_wrap(spk~sib_code) +
  geom_smooth(method = "lm",
              se = T,
              aes(color = gender_corr)) +
  scale_color_manual(values = cbPalette, name = "Gender")
```


### Phonetics
#### Speaker summaries (Accounting for creak)
```{r spk_sum}
exp_data$NC_range_semi <- exp_data$NC_pitMax_semi- exp_data$NC_pitMin_semi
exp_data$NC_range_Hz <- exp_data$NC_pitMax_Hz - exp_data$NC_pitMin_Hz
#exp_data$spk <- relevel(exp_data$spk, ref = "A")

df_no_control <- subset.data.frame(exp_data, sib_code != "control")
#df_no_control$spk <- relevel(df_no_control$spk, ref = "A")
df_no_control$sib_code <- relevel(df_no_control$sib_code, ref = "backed")

exp_summary_phon <- df_no_control %>% group_by(spk) %>% summarize("avg_f0_Hz"=mean(NC_pitAve_Hz), "avg_f0_semi"=mean(NC_pitAve_semi), "avg_f0_range_Hz" = mean(NC_range_Hz), "avg_f0_range_semi" = mean(NC_range_semi), "s_dur_ms" = mean(s_milliseconddur, na.rm = T), "avg_creak_prop" = mean(prop_creak), "avg_speech_rate" = mean(speech_rate)) 

print(exp_summary_phon)

violin_sib_mean_pitch <- ggplot(df_no_control, aes(x = spk, y = NC_pitAve_semi))+
  geom_violin(aes(fill=spk))+
  ylab("Mean F0 (Semitones, rel. 100 Hz)")+
  xlab("Speaker") +
  scale_fill_manual(values = cbPalette_2) 
print(violin_sib_mean_pitch)
ggsave(file="~/qp1_2spk/analysis/figures/violin_sib_mean_pitch.pdf",width=6,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/violin_sib_mean_pitch.png",width=6,height=4)

violin_sib_var_pitch <- ggplot(df_no_control, aes(x = spk, y = NC_range_semi))+
  geom_violin(aes(fill=spk))+
  ylab("F0 Range (Semitones, rel. 100 Hz)")+
  xlab("Speaker") +
  scale_fill_manual(values = cbPalette_2) 
print(violin_sib_var_pitch)
ggsave(file="~/qp1_2spk/analysis/figures/violin_sib_var_pitch.pdf",width=6,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/violin_sib_var_pitch.png",width=6,height=4)

violin_creak <- ggplot(df_no_control, aes(x = spk, y = prop_creak))+
  geom_violin(aes(fill=spk))+
  ylab("Proportion of Creak in Utterance")+
  xlab("Speaker") +
  scale_fill_manual(values = cbPalette_2) 
print(violin_creak)
ggsave(file="~/qp1_2spk/analysis/figures/violin_creak.pdf",width=6,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/violin_creak.png",width=6,height=4)

box_sib_mean_pitch <- ggplot(df_no_control, aes(x = spk, y = NC_pitAve_semi))+
  geom_boxplot(aes(fill=spk))+
  ylab("Mean F0 (Semitones, rel. 100 Hz)")+
  xlab("Speaker") +
  scale_fill_manual(values = cbPalette_2) 
print(box_sib_mean_pitch)
ggsave(file="~/qp1_2spk/analysis/figures/box_sib_mean_pitch.pdf",width=6,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/box_sib_mean_pitch.png",width=6,height=4)

box_sib_var_pitch <- ggplot(df_no_control, aes(x = spk, y = NC_range_semi))+
  geom_boxplot(aes(fill=spk))+
  ylab("F0 Range (Semitones, rel. 100 Hz)")+
  xlab("Speaker") +
  scale_fill_manual(values = cbPalette_2) 
print(box_sib_var_pitch)
ggsave(file="~/qp1_2spk/analysis/figures/box_sib_var_pitch.pdf",width=6,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/box_sib_var_pitch.png",width=6,height=4)

box_creak <- ggplot(df_no_control, aes(x = spk, y = prop_creak))+
  geom_boxplot(aes(fill=spk))+
  ylab("Proportion of Creak in Utterance")+
  xlab("Speaker") +
  scale_fill_manual(values = cbPalette_2) 
print(box_creak)
ggsave(file="~/qp1_2spk/analysis/figures/box_creak.pdf",width=6,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/box_creak.png",width=6,height=4)

box_rate <- ggplot(df_no_control, aes(x = spk, y = speech_rate))+
  geom_boxplot(aes(fill=spk))+
  ylab("Speech Rate (Syllables/Sec)")+
  xlab("Speaker") +
  scale_fill_manual(values = cbPalette_2) 
print(box_rate)
ggsave(file="~/qp1_2spk/analysis/figures/box_rate.pdf",width=6,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/box_rate.png",width=6,height=4)
```

#### Raw pitch measurements 

```{r raw_pitch, echo=FALSE}
smooth_pitch_Hz <- ggplot(exp_data,aes(x = pitAve_Hz, y = response_numeric/100))+
  geom_smooth(aes(colour=sib_code))+ 
  ylab("Masculinity Rating") +
  xlab("Mean Pitch (Hz)") + 
  scale_color_manual(values=cbPalette, name = "Sibilant Condition") 
print(smooth_pitch_Hz)
ggsave(file="~/qp1_2spk/analysis/figures/smooth_pitch_Hz.pdf",width=6,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/smooth_pitch_Hz.png",width=6,height=4)

smooth_pitch_semi <- ggplot(exp_data,aes(x = pitAve_semi, y = response_numeric/100))+
  geom_smooth(aes(colour=sib_code))+ 
  ylab("Masculinity Rating") +
  xlab("Mean Pitch (semitones)") +
  scale_color_manual("Sibilant Condition", values=cbPalette) 
print(smooth_pitch_semi)
ggsave(file="~/qp1_2spk/analysis/figures/smooth_pitch_semi.pdf",width=6,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/smooth_pitch_semi.png",width=6,height=4)

smooth_sd_pitch_Hz <- ggplot(exp_data,aes(x = pitSD_Hz, y = response_numeric/100))+
  geom_smooth(aes(colour=sib_code))+ 
  ylab("Masculinity Rating") +
  xlab("Pitch SD (Hz)") +
  scale_color_manual("Sibilant Condition", values=cbPalette) 
print(smooth_sd_pitch_Hz)
ggsave(file="~/qp1_2spk/analysis/figures/smooth_sd_pitch_Hz.pdf",width=6,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/smooth_sd_pitch_Hz.png",width=6,height=4)

smooth_sd_pitch_semi <- ggplot(exp_data,aes(x = pitSD_semi, y = response_numeric/100))+
  geom_smooth(aes(colour=sib_code))+ 
  ylab("Masculinity Rating") +
  xlab("Pitch SD (semitones)") +
  scale_color_manual("Sibilant Condition", values=cbPalette) 
print(smooth_sd_pitch_semi)
ggsave(file="~/qp1_2spk/analysis/figures/smooth_sd_pitch_semi.pdf",width=6,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/smooth_sd_pitch_semi.png",width=6,height=4)

smooth_range_pitch_Hz <- ggplot(exp_data,aes(x = (pitMax_Hz - pitMin_Hz), y = response_numeric/100))+
  geom_smooth(aes(colour=sib_code))+ 
  ylab("Masculinity Rating") +
  xlab("Pitch Range (Hz)") +
  scale_color_manual("Sibilant Condition", values=cbPalette) 
print(smooth_range_pitch_Hz)
ggsave(file="~/qp1_2spk/analysis/figures/smooth_range_pitch_Hz.pdf",width=6,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/smooth_range_pitch_Hz.png",width=6,height=4)

smooth_range_pitch_semi <- ggplot(exp_data,aes(x = (pitMax_semi - pitMin_semi), y = response_numeric/100))+
  geom_smooth(aes(colour=sib_code))+ 
  ylab("Masculinity Rating") +
  xlab("Pitch Range (semitones)") +
  scale_color_manual("Sibilant Condition", values=cbPalette) 
print(smooth_range_pitch_semi)
ggsave(file="~/qp1_2spk/analysis/figures/smooth_range_pitch_semi.pdf",width=6,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/smooth_range_pitch_semi.png",width=6,height=4)

ggplot(df_no_control, aes(y = response_numeric/100, 
                          x =(norm_max_f0 - norm_min_f0) )) + 
  stat_summary(aes(group = sib_code,
                   color = sib_code),
               fun = "mean",
               geom = "pointrange",
               alpha = .5) +
  xlab("Pitch Range (semitones)") +
  ylab("Speaker Masculinity Rating") + 
  facet_wrap(~spk) +
  geom_smooth(method = "lm",
              se = T,
              color = "black") +
  scale_color_manual(values = cbPalette_3, name = "Sibilant Condition")
ggsave(file="~/qp1_2spk/analysis/figures/pit_range_point.pdf",width=6,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/pit_range_point.png",width=6,height=4)

ggplot(df_no_control, aes(y = response_numeric/100, 
                          x =norm_mean_f0)) + 
  stat_summary(aes(group = sib_code,
                   color = sib_code),
               fun = "mean",
               geom = "pointrange",
               alpha = .5) +
  xlab("Mean Pitch (Semitones, rel. 100 Hz)") +
  ylab("Masculinity Rating") + 
  facet_wrap(~spk) +
  geom_smooth(method = "lm",
              se = T,
              color = "black") +
  scale_color_manual(values = cbPalette_3, name = "Sibilant Condition")
ggsave(file="~/qp1_2spk/analysis/figures/pit_ave_point.pdf",width=6,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/pit_ave_point.png",width=6,height=4)
```
#### No-creak pitch measurements 

```{r NC_pitch, echo=FALSE}
fig.smooth_nc_pitch_Hz <- ggplot(df.numeric,
                             aes(x = NC_pitAve_Hz,
                                 y = response))+
  geom_smooth(aes(colour=sib_code))+ 
  ylab("Masculinity Rating") +
  xlab("Mean Pitch (Hz) - Creak Excluded") + 
  scale_color_manual(values=cbPalette, 
                     name = "Sibilant Condition") 
print(fig.smooth_nc_pitch_Hz)
ggsave(file="~/qp1_2spk/analysis/figures/smooth_nc_pitch_Hz.pdf",
       width=6,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/smooth_nc_pitch_Hz.png",
       width=6,height=4)

fig.point_nc_pitch_Hz <- ggplot(df.numeric, 
                            aes(x = NC_pitAve_Hz, 
                                y = response)) + 
  geom_point() + 
  facet_grid(.~sib_code) + 
  geom_smooth(method = "lm", 
              aes(color = sib_code))
print(fig.point_nc_pitch_Hz)
ggsave(file="~/qp1_2spk/analysis/figures/point_nc_pitch_Hz.pdf",
       width=6,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/point_nc_pitch_Hz.png",
       width=6,height=4)

fig.smooth_nc_pitch_semi <- ggplot(df.numeric,
                               aes(x = NC_pitAve_semi, 
                                   y = response))+
  geom_smooth(aes(colour=sib_code))+ 
  ylab("Masculinity Rating") +
  xlab("Mean Pitch (semitones) - Creak Excluded") +
  scale_color_manual("Sibilant Condition", 
                     values=cbPalette) 
print(fig.smooth_nc_pitch_semi)
ggsave(file="~/qp1_2spk/analysis/figures/smooth_nc_pitch_semi.pdf",
       width=6,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/smooth_nc_pitch_semi.png",
       width=6,height=4)

fig.point_nc_pitch_semi <- ggplot(df.numeric, 
                                  aes(x = NC_pitAve_semi, 
                                      y = response)) + 
  geom_point() + 
  facet_grid(.~sib_code) + 
  geom_smooth(method = "lm", 
              aes(color = sib_code))
print(fig.point_nc_pitch_semi)
ggsave(file="~/qp1_2spk/analysis/figures/point_nc_pitch_semi.pdf",
       width=6,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/point_nc_pitch_semi.png",
       width=6,height=4)

smooth_sd_nc_pitch_Hz <- ggplot(exp_data,aes(x = NC_pitSD_Hz, y = response_numeric/100))+
  geom_smooth(aes(colour=sib_code))+ 
  ylab("Masculinity Rating") +
  xlab("Pitch SD (Hz) - Creak Excluded") +
  scale_color_manual("Sibilant Condition", values=cbPalette) 
print(smooth_sd_nc_pitch_Hz)
ggsave(file="~/qp1_2spk/analysis/figures/smooth_sd_nc_pitch_Hz.pdf",width=6,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/smooth_sd_nc_pitch_Hz.png",width=6,height=4)

point_sd_nc_pitch_Hz <- ggplot(exp_data, aes(x =NC_pitSD_Hz, y = response_numeric/100)) + 
  geom_point() + 
  facet_grid(.~sib_code) + 
  geom_smooth(method = "lm", aes(color = sib_code))
print(point_sd_nc_pitch_Hz)

smooth_sd_nc_pitch_semi <- ggplot(exp_data,aes(x = NC_pitSD_semi, y = response_numeric/100))+
  geom_smooth(aes(colour=sib_code))+ 
  ylab("Masculinity Rating") +
  xlab("Pitch SD (semitones) - Creak Excluded") +
  scale_color_manual("Sibilant Condition", values=cbPalette) 
print(smooth_sd_nc_pitch_semi)
ggsave(file="~/qp1_2spk/analysis/figures/smooth_sd_nc_pitch_semi.pdf",width=6,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/smooth_sd_nc_pitch_semi.png",width=6,height=4)

point_sd_nc_pitch_semi <- ggplot(exp_data, aes(x =NC_pitSD_semi, y = response_numeric/100)) + 
  geom_point() + 
  facet_grid(.~sib_code) + 
  geom_smooth(method = "lm", aes(color = sib_code))
print(point_sd_nc_pitch_semi)

smooth_range_nc_pitch_Hz <- ggplot(exp_data,aes(x = (NC_pitMax_Hz - NC_pitMin_Hz), y = response_numeric/100))+
  geom_smooth(aes(colour=sib_code))+ 
  ylab("Masculinity Rating") +
  xlab("Pitch Range (Hz) - Creak Excluded") +
  scale_color_manual("Sibilant Condition", values=cbPalette) 
print(smooth_range_nc_pitch_Hz)
ggsave(file="~/qp1_2spk/analysis/figures/smooth_range_nc_pitch_Hz.pdf",width=6,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/smooth_range_nc_pitch_Hz.png",width=6,height=4)

point_range_nc_pitch_Hz <- ggplot(exp_data, aes(x =(NC_pitMax_Hz - NC_pitMin_Hz), y = response_numeric/100)) + 
  geom_point() + 
  facet_grid(.~sib_code) + 
  geom_smooth(method = "lm", aes(color = sib_code))
print(point_range_nc_pitch_Hz)

smooth_range_nc_pitch_semi <- ggplot(exp_data,aes(x = (NC_pitMax_semi - NC_pitMin_semi), y = response_numeric/100))+
  geom_smooth(aes(colour=sib_code))+ 
  ylab("Masculinity Rating") +
  xlab("Pitch Range (semitones) - Creak Excluded") +
  scale_color_manual("Sibilant Condition", values=cbPalette) 
print(smooth_range_nc_pitch_semi)
ggsave(file="~/qp1_2spk/analysis/figures/smooth_range_nc_pitch_semi.pdf",width=6,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/smooth_range_nc_pitch_semi.png",width=6,height=4)

point_range_nc_pitch_semi <- ggplot(exp_data, aes(x =(NC_pitMax_semi - NC_pitMin_semi), y = response_numeric/100)) + 
  geom_point() + 
  facet_grid(.~sib_code) + 
  geom_smooth(method = "lm", aes(color = sib_code))
print(point_range_nc_pitch_semi)
```

#### Role of creak

At first, it appears like creak plays a large role in predicting masculinity rating, but this perceived effect diminishes when accounting for things like speaker ID and sibilant condition.   

```{r creak_bar, echo=FALSE}
exp_data_creak <- filter(exp_data) %>%
  group_by(creak) %>%
  summarise( 
    n=n(),
    mean=mean(response_numeric/100),
    sd=sd(response_numeric/100)
  ) %>%
  mutate( se=sd/sqrt(n))  %>%
  mutate( ic=se * qt((1-0.05)/2 + .5, n-1))
bar_all_by_creak <- ggplot(exp_data_creak, aes(x = creak, y = mean)) +
  stat_summary(fun = mean, geom = "bar", position = position_dodge(width = .9),
               size = 3) +
  geom_errorbar(aes(ymin=mean-ic, 
                    ymax=mean+ic), width=0.3, position = position_dodge(width = .9)) + 
  ylab("Masculinity Rating") +
  xlab("Creak Present?") 
ggsave(file="~/qp1_2spk/analysis/figures/bar_all_by_creak.pdf",width=6,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/bar_all_by_creak.png",width=6,height=4)
print(bar_all_by_creak)

exp_data_creak_spk <- filter(exp_data) %>%
  group_by(spk,creak) %>%
  summarise( 
    n=n(),
    mean=mean(response_numeric/100),
    sd=sd(response_numeric/100)
  ) %>%
  mutate( se=sd/sqrt(n))  %>%
  mutate( ic=se * qt((1-0.05)/2 + .5, n-1))
bar_by_spk_creak <- ggplot(exp_data_creak_spk, aes(x = spk, y = mean, fill = creak)) +
  stat_summary(fun = mean, geom = "bar", position = position_dodge(width = .9),
               size = 3) +
  geom_errorbar(aes(ymin=mean-ic, 
                    ymax=mean+ic), width=0.3, position = position_dodge(width = .9)) + 
  ylab("Masculinity Rating") +
  xlab("Speaker") + 
  scale_fill_manual(values = c("red","lightgreen"), name = "Creak Present?")
ggsave(file="~/qp1_2spk/analysis/figures/bar_by_spk_creak.pdf",width=6,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/bar_by_spk_creak.png",width=6,height=4)
print(bar_by_spk_creak)

smooth_creak <- ggplot(exp_data,aes(x = prop_creak, y = response_numeric/100))+
  geom_smooth(aes(colour=sib_code))+ 
  ylab("Masculinity Rating") +
  xlab("Proportion of Creak within Utterance") + 
  scale_color_manual(values=cbPalette, name = "Sibilant Condition") 
print(smooth_creak)
ggsave(file="~/qp1_2spk/analysis/figures/smooth_creak.pdf",width=6,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/smooth_creak.png",width=6,height=4)

smooth_creak_point <- ggplot(exp_data, aes(x =prop_creak, y = response_numeric/100)) + 
  geom_point() + 
  facet_grid(~spk) +
  geom_smooth(method = "lm", aes()) + 
  ylab("Masculinity Rating") +
  xlab("Proportion of Creak within Utterance")
print(smooth_creak_point)

df_no_control <- subset.data.frame(exp_data, sib_code != "control")
df_no_control$spk <- relevel(df_no_control$spk, ref = "A")
df_no_control$sib_code <- relevel(df_no_control$sib_code, ref = "backed")
ggplot(df_no_control, aes(y = response_numeric/100, 
                          x = prop_creak)) + 
  stat_summary(aes(group = sib_code,
                   color = sib_code),
               fun = "mean",
               geom = "pointrange",
               alpha = .5) +
  xlab("Proportion Creak") +
  ylab("Masculinity Rating") + 
  facet_wrap(~spk) +
  geom_smooth(method = "lm",
              se = T,
              color = "black") +
  scale_color_manual(values = cbPalette_3, name = "Sibilant Condition")
ggsave(file="~/qp1_2spk/analysis/figures/prop_creak_point.pdf",width=6,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/prop_creak_point.png",width=6,height=4)

```

```{r}
ggplot(df.numeric, mapping = aes(y = response, 
                          x = prop_creak)) + 
  stat_summary(aes(group = spk),
               fun = "mean",
               geom = "pointrange",
               alpha = .25) +
  xlab("Proportion of Creak in Utterance") +
  ylab("Mean Masculinity Rating") + 
  facet_wrap(~spk) +
  geom_smooth(method = "lm",
              se = T,
              color = "red") +
  scale_color_manual(values = cbPalette, name = "Sibilant Condition")
```


#### Sibilant Duration

```{r sib_dur, echo = FALSE}
sib_dur <- ggplot(exp_data,aes(x = s_milliseconddur, y = response_numeric/100))+
  geom_smooth(aes(colour=sib_code))+ 
  ylab("Masculinity Rating") +
  xlab("/s/ Duration (ms)") +
  scale_color_manual("Sibilant Condition", values=cbPalette) 
print(sib_dur)
ggsave(file="~/qp1_2spk/analysis/figures/sib_dur.pdf",width=6,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/sib_dur.png",width=6,height=4)

sib_dur_point <- ggplot(exp_data, aes(x =s_milliseconddur, y = response_numeric/100)) + 
  geom_point() + 
  geom_smooth(method = "lm", aes(color = sib_code))
print(sib_dur_point)

exp_data_sdur <- filter(exp_data) %>% filter(!is.na(s_milliseconddur)) %>%
  group_by(spk) %>%
  summarise( 
    n=n(),
    mean=mean(s_milliseconddur),
    sd=sd(s_milliseconddur)
  ) %>%
  mutate( se=sd/sqrt(n))  %>%
  mutate( ic=se * qt((1-0.05)/2 + .5, n-1))

bar_by_sdur <- ggplot(exp_data_sdur, aes(x = spk, y = mean)) +
  stat_summary(fun = mean, geom = "bar", position = position_dodge(width = .9),
               size = 3) +
  geom_errorbar(aes(ymin=mean-ic, 
                    ymax=mean+ic), width=0.3, position = position_dodge(width = .9)) + 
  ylab("/s/ Duration (ms)") +
  xlab("Speaker") 
#ggsave(file="~/qp1_2spk/analysis/figures/bar_by_sdur.pdf",width=6,height=4)
#ggsave(file="~/qp1_2spk/analysis/figures/bar_by_sdur.png",width=6,height=4)
print(bar_by_sdur)

sib_dur_box <- ggplot(exp_data, aes(x =spk, y = s_milliseconddur)) + 
  geom_boxplot() 
print(sib_dur_box)


```

#### Speech Rate
```{r}
ggplot(df.numeric, 
       mapping = aes(y = response, 
                          x = speech_rate)) + 
  stat_summary(aes(group = spk),
               fun = "mean",
               geom = "pointrange",
               alpha = .25) +
  xlab("Speech Rate (syllables per sec) of Utterance") +
  ylab("Mean Masculinity Rating") + 
  facet_wrap(~spk) +
  geom_smooth(method = "lm",
              se = T,
              color = "red") +
  scale_color_manual(values = cbPalette, name = "Sibilant Condition")
```


#### Raw F2
```{r f2, echo=FALSE}
df_no_control <- subset.data.frame(exp_data, sib_code != "control")
df_no_control$spk <- as.factor(df_no_control$spk)
df_no_control$spk <- relevel(df_no_control$spk, ref = "A")
df_no_control$sib_code <- relevel(df_no_control$sib_code, ref = "backed")

box_f2 <- ggplot(df_no_control, aes(x = spk, y = f2_raw))+
  geom_point(aes(color=spk),
             position = position_dodge())+
  ylab("Raw F2")+
  xlab("Speaker") +
  facet_wrap(~vowel) +
  scale_fill_manual(values = cbPalette_2) 
print(box_f2)

resp_by_f2 <- ggplot(exp_data, aes(x = response_numeric/100, y = f2_raw)) + 
  geom_point(aes(colour =spk)) + 
  ylab("Raw F2") +
  xlab("Speaker Masculinity Rating") + 
  scale_color_manual(values = cbPalette)
print(resp_by_f2)

ggplot(df.numeric, 
       aes(y = response, 
           x = f2_norm)) + 
  stat_summary(aes(group = spk,
                   color = spk),
               fun = "mean",
               geom = "pointrange",
               alpha = .5) +
  xlab("Raw F2") +
  ylab("Masculinity Rating") + 
  facet_wrap(spk~sib_code) +
  geom_smooth(method = "lm",
              se = T,
              color = "black") #+
  #scale_color_manual(values = cbPalette_3, name = "Sibilant Condition")
ggsave(file="~/qp1_2spk/analysis/figures/df_no_control.pdf",width=6,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/df_no_control.png",width=6,height=4)
print(resp_by_f2_v2)
```

## Modeling
### Confirm that Linear Model is Inappropriate for Data 
```{r}
df.numeric_s <- filter(df.numeric, 
                       sib_code != "control")
fit.lmer <- lmer(response ~ sib_code*spk*s_msC*f2_raw +
                   prop_creakC + 
                   #speech_rateC + 
                   NC_norm_mean_f0C + 
                   NC_norm_range_f0C +
                   (1 | workerid) + 
                   (1 | triplet_id), 
                 data = df.numeric_s,
                 REML = F)
summary(fit.lmer)

# Check distributions of residuals - evidence of heterosketasticity
df.numeric_s %>% 
  ungroup() %>% 
  mutate(predicted = predict(fit.lmer, 
                             newdata = df.numeric_s, 
                             type = "response", 
                             re.form = NA),
         residuals = residuals(fit.lmer)) %>%
  ggplot(mapping = aes(x = predicted, 
                       y = residuals)) +
  geom_point(alpha = 0.05) +
  geom_smooth(method = "loess", 
              color = "red") +
  labs(title = "Residuals vs. fitted values of linear mixed effects model") 

fit.lmer %>% 
  augment() %>% 
  ggplot(mapping = aes(sample = scale(.resid))) +
  geom_qq_line() + 
  geom_qq() + 
  labs(title = "QQ Plot")

qqnorm(resid(fit.lmer))
qqline(resid(fit.lmer), col = "red")
```

### ZOIB Model using `brm()`
```{r}
# build ZOIB model
l.zoib <- bf(response ~ gender_corr*spk*srq_scoreC +
               sib_code +
               spk +
               sib_code:spk + 
               srq_scoreC + 
               gender_corr + 
               prop_creakC + 
               speech_rateC + 
               NC_norm_mean_f0C +
               NC_norm_mean_f0C + 
               NC_norm_range_f0C +
               (1 | workerid) + 
               (1 | triplet_id),
             phi ~ gender_corr*spk, 
             zoi ~ gender_corr*spk,
             coi ~ gender_corr*spk,
             family = zero_one_inflated_beta()
)

# set priors - all weakly informed, default student_t priors for all random eff. (not shown)
priors <- c(
  # prior for the response variable 
  ## main effects
  prior(normal(-0.7, 0.5), 
        class = "b", 
        coef = "spkB"), # Main effect of spkB vs ref
  prior(normal(0, 0.5), 
        class = "b", 
        coef = "sib_codebacked"), # Main effect of backed vs ref
  prior(normal(0, 0.5), 
        class = "b", 
        coef = "sib_codemid"), # Main effect of mid vs ref
  prior(normal(0, 0.5), 
        class = "b", 
        coef = "sib_codefronted"), # Main effect of fronted vs ref
    prior(normal(0, 0.5),
        class = "b",
        coef = "srq_scoreC"), # Main effect of srq score
    prior(normal(0, 0.5),
        class = "b",
        coef = "gender_corrmale"), # Main effect of listener gender (male)
  prior(normal(0, 0.5),
        class = "b",
        coef = "gender_corrnc"), # Main effect of listener gender (nc)
  prior(normal(0, 0.5),
        class = "b",
        coef = "prop_creakC"), # Main effect of prop_creak
  prior(normal(0, 0.5),
        class = "b",
        coef = "NC_norm_mean_f0C"), # Main effect of mean pitch
  prior(normal(0, 0.5),
        class = "b",
        coef = "NC_norm_range_f0C"), # Main effect of pitch variability
  prior(normal(0, 0.5),
        class = "b",
        coef = "speech_rateC"), # Main effect of speech rate
  ## interactions 
  prior(normal(0, 0.5), 
        class = "b", 
        coef = "spkB:sib_codebacked"), # spkB:backed interaction
  prior(normal(0, 0.5), 
        class = "b", 
        coef = "spkB:sib_codemid"), # spkB:mid interaction
  prior(normal(0, 0.5), 
        class = "b", 
        coef = "spkB:sib_codefronted"), # spkB:fronted interaction
  prior(normal(0, 0.5), 
        class = "b", 
        coef = "gender_corrmale:spkB"), # gender_corr:spk interaction term
  prior(normal(0, 0.5), 
        class = "b", 
        coef = "gender_corrmale:spkB:srq_scoreC"), # gender_corr:spk:srq interaction term
  prior(normal(0, 0.5), 
        class = "b", 
        coef = "gender_corrmale:srq_scoreC"), # gender_corr:srq interaction term
  ##
  prior(normal(0, 0.5), 
        class = "b", 
        coef = "gender_corrnc:spkB"), # gender_corr:spk interaction term
  prior(normal(0, 0.5), 
        class = "b", 
        coef = "gender_corrnc:spkB:srq_scoreC"), # gender_corr:spk:srq interaction term
  prior(normal(0, 0.5), 
        class = "b", 
        coef = "gender_corrnc:srq_scoreC"), # gender_corr:srq interaction term
  prior(normal(0, 0.5),
        class = "b",
        coef = "spkB:srq_scoreC"),
  
  # priors for random effects 
  prior(student_t(3, 0, 1), 
        class = "sd", 
        group = "workerid"), # Random intercept for workerid
  prior(student_t(3, 0, 1), 
        class = "sd", 
        group = "triplet_id"), # Random intercept for triplet_id

  # priors for phi (precision parameter)
  prior(normal(6, 2), 
        class = "Intercept", 
        dpar = "phi"),    # weakly informative, log-phi
  prior(normal(0,0.5),
        class = "b",
        dpar = "phi",
        coef = "spkB"), # Effect of spkB on phi
  prior(normal(0,0.5),
        class = "b",
        dpar = "phi",
        coef = "gender_corrmale"), # Effect of gender_corrmale on phi
  prior(normal(0,0.5),
        class = "b",
        dpar = "phi",
        coef = "gender_corrnc"), # Effect of gender_corrnc on phi
  prior(normal(0,0.5),
        class = "b",
        dpar = "phi",
        coef = "gender_corrmale:spkB"), # Effect of gender_corrnc:spkB on phi
  prior(normal(0,0.5),
        class = "b",
        dpar = "phi",
        coef = "gender_corrnc:spkB"), # Effect of gender_corrnc:spkB on phi

  # priors for zero-one inflation parameters
  prior(normal(-4, 1), 
        class = "Intercept", 
        dpar = "zoi"),  # Updated prior for zoi
  prior(normal(-5, 1), 
        class = "Intercept", 
        dpar = "coi"),  # Updated prior for coi
  prior(normal(0, 0.5), 
        class = "b", 
        dpar = "zoi", 
        coef = "spkB"),  # Effect of spkB on zero-inflation
  prior(normal(0, 0.5), 
        class = "b", 
        dpar = "coi", 
        coef = "spkB"),  # Effect of spkB on one-inflation
  prior(normal(0, 0.5), 
        class = "b", 
        dpar = "zoi", 
        coef = "gender_corrmale"),  # Effect of spkB on zero-inflation
  prior(normal(0, 0.5), 
        class = "b", 
        dpar = "coi", 
        coef = "gender_corrmale"),  # Effect of spkB on one-inflation
  prior(normal(0, 0.5), 
        class = "b", 
        dpar = "zoi", 
        coef = "gender_corrnc"),  # Effect of spkB on zero-inflation
  prior(normal(0, 0.5), 
        class = "b", 
        dpar = "coi", 
        coef = "gender_corrnc"),  # Effect of spkB on one-inflation
  prior(normal(0, 0.5), 
        class = "b", 
        dpar = "zoi", 
        coef = "gender_corrmale:spkB"),  # Effect of spkB on zero-inflation
  prior(normal(0, 0.5), 
        class = "b", 
        dpar = "coi", 
        coef = "gender_corrmale:spkB"),  # Effect of spkB on one-inflation
  prior(normal(0, 0.5), 
        class = "b", 
        dpar = "zoi", 
        coef = "gender_corrnc:spkB"),  # Effect of spkB on zero-inflation
  prior(normal(0, 0.5), 
        class = "b", 
        dpar = "coi", 
        coef = "gender_corrnc:spkB")  # Effect of spkB on one-inflation
)

# prior predictive checks (do this before fitting model)
fit.zoib_prior <- brm(
  formula = l.zoib,
  data = df.numeric,         
  prior = priors,
  sample_prior = "only",     
  iter = 8000,
  warmup = 2000,
  cores = 4,
  chains = 8,
  seed = 327,
  control = list(adapt_delta = 0.99),
  file = "brm_zoib_prior")
```

```{r}
# INITIAL fit zoib model using brm()
fit.zoib <- brm(
  formula = l.zoib,
  data = df.numeric,
  prior = priors,
  iter = 6000,
  warmup = 2000,
  cores = 2,
  chains = 8,
  file = "brm_zoib_1",
  init_r = 0.1,
  control = list(adapt_delta = 0.99),
  seed = 327,
)

# LOAD fit zoib model 
#fit.zoib <- readRDS("~/qp1_2spk/brm_zoib_3rd.rds")

summary(fit.zoib)
```



#### Check Bayesian Model Assumptions 
```{r}
# check model fit - plot fit 
plot(fit.zoib) 
ggsave(file="~/qp1_2spk/analysis/figures/zoib_fit.pdf")
```

```{r}
# check model fit - posterior predictive check 
pp_check(fit.zoib, ndraws = 100)
ggsave(file="~/qp1_2spk/analysis/figures/pp_check.pdf",
       width=8,height=4)
```

```{r}
# plot observed data
#print(fig.bar_sib)

# plot posterior predictions 
fig.bar_sib_post_alt <- df.numeric %>% 
  add_predicted_draws(object = fit.zoib, # generate predictions from posterior
                      ndraws = 1) %>% 
  ggplot(mapping = aes(x = sib_code, 
                       y = .prediction)) +
  stat_summary(fun = "mean",
               geom = "bar",
               fill = "pink") + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") +
  scale_x_discrete(limits = c("control", "backed", "mid", "fronted")) + 
  labs(x = "/s/ Condition",
       y = "Masculinity Rating") + 
  facet_grid(spk~gender_corr)

fig.bar_sib_post <- df.numeric %>% 
  add_predicted_draws(object = fit.zoib, # generate predictions from posterior
                      ndraws = 1) %>% 
  ggplot(mapping = aes(x = sib_code, 
                       y = .prediction)) +
  stat_summary(fun = "mean",
               geom = "bar",
               fill = "pink") + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") +
  scale_x_discrete(limits = c("control", "backed", "mid", "fronted")) + 
  labs(x = "/s/ Condition",
       y = "Masculinity Rating",
       title = "Posterior Masculinity Ratings") + 
  facet_grid(spk~gender_corr)

ggsave(file="~/qp1_2spk/analysis/figures/s_post_bar.pdf",
       width=8,height=4)

# plot priors
fig.bar_sib_prior <- df.numeric %>% 
  add_predicted_draws(object = fit.zoib_prior, # generate predictions from priors
                      ndraws = 1) %>%  
  ggplot(mapping = aes(x = sib_code, 
                       y = .prediction)) +
  stat_summary(fun = "mean",
               geom = "bar",
               fill = "lightgreen") + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") + 
  scale_x_discrete(limits = c("control", "backed", "mid", "fronted")) + 
  labs(title = "Prior distribution of masculinity ratings by /s/ condition",
       x = "/s/ Condition",
       y = "Masculinity Rating")

ggsave(file="~/qp1_2spk/analysis/figures/s_prior_bar.pdf",
       width=8,height=4)

fig.by_gender
fig.bar_sib_post_alt + fig.bar_sib_post
```

### Hypothesis Testing
#### Speaker Differences 
```{r}
h1 <- hypothesis(fit.zoib, "Intercept > Intercept + spk B") 

df.test1 <- rbind(data.frame(Hypothesis = "Spk A > Spk B", h1$hypothesis)) %>% 
  select(-Hypothesis.1)

kable(df.test1)
```


#### /s/ Condition Differences
```{r}
fit.zoib %>% 
  emmeans(specs = pairwise ~ sib_code | spk) %>% 
  pluck("contrasts") %>% 
  gather_emmeans_draws() %>% 
  ggplot(aes(x = .value,
             y = spk,
             fill = after_stat(x > 0))) + 
  facet_wrap(~ contrast) +
  stat_halfeye(point_interval = mean_hdi,
               .width = c(0.5, 0.75, 0.95),
               show.legend = T) + 
  geom_vline(xintercept = 0, 
             linetype = 2) + 
  scale_fill_manual(values = c("gray80", "skyblue")) + 
  scale_x_continuous(limits = c(-0.15, 0.25)) +
  labs(title = "Pairwise comparisons of /s/ condition by speaker (single token)",
       y = "speaker")
ggsave(file="~/qp1_2spk/analysis/figures/emmeans.pdf", width=8,height=4)
ggsave(file="~/qp1_2spk/analysis/figures/emmeans.png", width=8,height=4)
```

```{r}
sib.h1 <- hypothesis(fit.zoib, "Intercept > Intercept + sib_codefronted") 
sib.h2 <- hypothesis(fit.zoib, "Intercept + sib_codemid > Intercept + sib_codefronted")
sib.h3 <- hypothesis(fit.zoib, "Intercept + sib_codebacked > Intercept + sib_codefronted")

df.sib.test <- rbind(data.frame(Hypothesis = "Control > Fronted /s/", 
                                sib.h1$hypothesis),
                     data.frame(Hypothesis = "Mid /s/ > Fronted /s/", 
                                sib.h2$hypothesis),
                     data.frame(Hypothesis = "Backed /s/ > Fronted /s/", 
                                sib.h3$hypothesis)) %>% 
  select(-Hypothesis.1)

kable(df.sib.test)
```

##### Use if spk:sib_code interaction is in model
```{r}
sibA.h1 <- hypothesis(fit.zoib, "Intercept > Intercept + sib_codefronted") 
sibA.h2 <- hypothesis(fit.zoib, "Intercept + sib_codemid > Intercept + sib_codefronted")
sibA.h3 <- hypothesis(fit.zoib, "Intercept + sib_codebacked > Intercept + sib_codefronted")
sibB.h1 <- hypothesis(fit.zoib, "Intercept + spkB > Intercept + spkB + sib_codefronted + spkB:sib_codefronted") 
sibB.h2 <- hypothesis(fit.zoib, "Intercept + spkB + sib_codemid + spkB:sib_codemid > Intercept + spkB + sib_codefronted + spkB:sib_codefronted")
sibB.h3 <- hypothesis(fit.zoib, "Intercept + spkB + sib_codebacked + spkB:sib_codebacked > Intercept + spkB + sib_codefronted + spkB:sib_codefronted")

df.sib.test.mult <- rbind(data.frame(Hypothesis = "Spk A: Control > Fronted /s/", 
                                sibA.h1$hypothesis),
                     data.frame(Hypothesis = "Spk A: Mid /s/ > Fronted /s/", 
                                sibA.h2$hypothesis),
                     data.frame(Hypothesis = "Spk A: Backed /s/ > Fronted /s/", 
                                sibA.h3$hypothesis),
                     data.frame(Hypothesis = "Spk B: Control > Fronted /s/", 
                                sibB.h1$hypothesis),
                     data.frame(Hypothesis = "Spk B: Mid /s/ > Fronted /s/", 
                                sibB.h2$hypothesis),
                     data.frame(Hypothesis = "Spk B: Backed /s/ > Fronted /s/", 
                                sibB.h3$hypothesis)) %>% 
  select(-Hypothesis.1)

kable(df.sib.test.mult)
```

#### Phonetic Effects 
```{r}
phon.h1 <- hypothesis(fit.zoib, "prop_creakC > 0") 
phon.h2 <- hypothesis(fit.zoib, "NC_norm_mean_f0C < 0") 
phon.h3 <- hypothesis(fit.zoib, "NC_norm_range_f0C < 0") 
phon.h4 <- hypothesis(fit.zoib, "speech_rateC < 0")

df.phon.test <- rbind(data.frame(Hypothesis = "Creak Effect?", 
                                  phon.h1$hypothesis),
                       data.frame(Hypothesis = "Mean Pitch Effect?",
                                  phon.h2$hypothesis),
                       data.frame(Hypothesis = "Pitch Range Effect?",
                                  phon.h3$hypothesis),
                       data.frame(Hypothesis = "Speech Rate Effect?",
                                  phon.h4$hypothesis)) %>% 
  select(-Hypothesis.1)

kable(df.phon.test)
```

#### What drives difference? 
```{r}
fit.zoib %>% 
  emmeans(specs = pairwise ~ spk | gender_corr) %>% 
  ggplot(aes(x = .value,
             y = vowel)) + 
  facet_wrap(~ contrast) +
  geom_vline(xintercept = 0, 
             linetype = 2) + 
  labs(title = "Pairwise comparisons of /s/ condition by following vowel",
       y = "vowel")
ggsave(file="~/qp1_2spk/analysis/figures/emmeans.pdf", width=8,height=4)

fit.zoib %>% 
  emmeans(specs = pairwise ~ sib_code | gender_corr, lmerTest.limit = 29499) %>% 
  pluck("contrasts") %>% 
  summary() %>%
  ggplot(aes(x = estimate,
             y = gender_corr)) +
  geom_errorbar(aes(xmin=estimate - (SE * qt((1-0.05)/2 + .5, df)), 
                    xmax=estimate + (SE * qt((1-0.05)/2 + .5, df)),
                    width = .3)) + 
  geom_point(shape = 21,
             color = "black",
             fill = "lightblue") + 
  geom_vline(xintercept = 0, 
             linetype = 2) + 
  facet_wrap(~ contrast)
```

```{r}
emmeans(fit.lmer, 
        pairwise ~ sib_code | vowel_class * spk, 
        pbkrtest.limit = 9772) %>%
  pluck("contrasts") %>%
  as.data.frame() %>% 
  ggplot(aes(x = estimate,
             y = vowel_class, 
             group = spk)) + 
  geom_errorbar(aes(xmin=estimate - (SE * qt((1-0.05)/2 + .5, df)), 
                    xmax=estimate + (SE * qt((1-0.05)/2 + .5, df)),
                    width = .3)) + 
  geom_point(shape = 21,
             color = "black",
             fill = "lightblue") + 
  geom_vline(xintercept = 0, 
             linetype = 2) + 
  facet_grid(spk ~ contrast)
```

```{r}
contrast(
  emtrends(fit.lmer, ~ sib_code | spk, var = "f2_raw"),
  method = "pairwise"
)

emmip(fit.lmer, sib_code ~ f2_raw | spk, cov.reduce = range) +
  ggplot2::labs(x = "Vowel (continuous)", y = "Predicted response") +
  ggplot2::theme_minimal()
```

```{r}
# Create prediction grid
df.no_control <- df.numeric %>% filter(sib_code != "control")
df.no_control$sib_code <- factor(df.no_control$sib_code, 
                              levels = c("backed", 
                                         "mid", 
                                         "fronted"))
fit.lmer.mini <- lmer(response ~ f2_raw*spk*sib_code +
                   (1 | workerid) + 
                   (1 | triplet_id), 
                 data = df.no_control,
                 REML = F)

temp.df <- expand.grid(
  f2_raw = seq(min(df.no_control$f2_raw, na.rm = T), 
               max(df.no_control$f2_raw, na.rm = T), 
               length.out = 100),
  sib_code = levels(df.no_control$sib_code),
  spk = levels(df.no_control$spk),
  workerid = NA) # exclude random effects (fixed effects only)

temp.df$pred <- predict(fit.lmer.mini, newdata = temp.df, re.form = NA)

# Plot
ggplot(temp.df, aes(x = f2_raw, y = pred, group = spk, color = sib_code)) +
  geom_line(size = .5) +
  facet_wrap(~ spk) +
  labs(x = "Raw F2", y = "Predicted Response") +
  scale_x_continuous(trans = "reverse") + 
  theme_minimal()

ggplot(df.numeric,
       aes(x = f2_raw,
           y = response,
           color = sib_code)) + 
  #geom_point() + 
  geom_smooth(method = "lm") + 
  facet_grid(~ spk) + 
  scale_x_continuous(trans = "reverse") + 
  labs(title = "single token")
```

```{r}
df.numeric %>% 
  filter(sib_code != "control") %>%
  ggplot(aes(x = f2_norm,
             color = cog,
             shape = sib_code,
             y = response)) + 
  geom_smooth(method = "lm",
              color = "black",
              alpha = 0.2,
              se = T) +
    stat_summary(fun = "mean",
               geom = "point",
               alpha = 0.75) + 
  scale_color_gradient2(mid = "red",
                       low = "blue",
                       high = "yellow",
                       limits = c(4000, 9500),
                       midpoint = 7000) +
  coord_cartesian(ylim = c(0, 1)) + 
  scale_x_continuous(trans = "reverse") + 
  #facet_wrap(~spk)
  facet_grid(spk~sib_code)

df.numeric %>% 
  filter(sib_code != "control") %>%
  group_by(spk, sib_code, f2_raw) %>%
  summarise(
    cog = mean(cog, na.rm = T),
    response = mean(response, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  ggplot(aes(x = f2_raw,
             y = cog,
             shape = sib_code,
             color = response)) + 
  geom_point(alpha = 0.75) +
  scale_color_gradient2(mid = "red",
                        low = "blue",
                        high = "yellow",
                        limits = c(0, 1),
                        midpoint = 0.5) +
  coord_cartesian(ylim = c(4000, 9500)) + 
  scale_x_continuous(trans = "reverse") + 
  #facet_wrap(~spk)
  facet_grid(spk~sib_code)
```

```{r}
df.numeric %>% 
  filter(sib_code != "control") %>%
  ggplot(mapping = aes(x = sib_code,
                     y = response)) + 
  stat_summary(fun = "mean",
               geom = "bar",
               fill = "lightblue") + 
  stat_summary(fun.data = "mean_cl_boot",
               geom = "linerange") +
  facet_grid(spk~vowel_class) +
  scale_x_discrete(limits = c("backed", "mid", "fronted")) + 
  labs(x = "/s/ Condition",
       y = "Masculinity Rating", 
       title = "Single token: masc rating by /s/ + vowel class")
```

